Towards a miniKanren with fair search strategies

### 2019-05-26 Paper/paper.tex
LKC responds to notes

\NOTE[DPF]{``current'' was for BFSser if we need it, which we probably won't
since the re-emergence of BFSser.  So let's reserve the word just in case.}

@@

We devise two new search strategies (i.e. balanced interleaving DFS 
(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
implementation of \BFS. These strategies have different features 
in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
\disj{} and fair \conj{}.

@@

\NOTE[DPF]{Please leave ``prove'' (just here).}

>>>>

\NOTE[DPF]{``current'' was for BFSser if we need it, which we probably won't
since the re-emergence of BFSser.  So let's reserve the word just in case.}
\NOTE[LKC]{What do you mean by ``re-emergence''?}

@@

We devise two new search strategies (i.e., balanced interleaving DFS 
(\DFSbi{}) and fair DFS (\DFSf{})) and devise a new 
implementation of \BFS. These strategies have different features 
in fairness: \DFSbi{} has an almost-fair \disj{} and unfair \conj{}. 
\DFSf{} has fair \disj{} and unfair \conj{}. \BFS{} has both fair
\disj{} and fair \conj{}.

@@

\NOTE[DPF]{Please leave ``prove'' (just here).}
\NOTE[LKC]{OK. I won't touch it.}
